Section One

### 2020-07-28 new2020/sections/sec01.Rmd
Better build system

```{=latex}
\begin{equation}
\label{eq:no}
y = 2x
\end{equation}
```

Predicting bus arrival is ... quite something \( \cite{Elliott_2020} \)

I can just type things here, like ... yeah!
```{=latex}
\begin{equation}
\label{eq:hello}
x = \int 2x\; \mathrm{d}x
\end{equation}
```

We see in `\cref{eq:hello}`{=latex} that ... blah.

>>>>

* the problem of predicting bus arrival - it needs to use real-time traffic information @cite:cn;
* however, many deployed methods are either specific to a provider/city, or don't make use of real-time data (only vehicle position and/or arrival delays, e.g., in Auckland)
* since the only logical source of ``traffic data'' in this setting is the transit vehicles themselves, makes sense to develop framework that uses them to estimate real-time network state @cite:Elliott_2020;
* in this example, particle filter is used to obtain a sample of points from the arrival time distribution - many many points, which cannot possibly be distributed or stored efficiently
* we propose a method of reducing this to a simple discrete CDF of arrival time (in minutes)
